\thetitle\\ \vspace{0.2em} \LARGE{On The Inadequacy of Uniform Modeling for WLAN Workloads}

### 2008-01-20 models.tex
Itemize-based tabels for properties & models.

\begin{tabular}{|c|l|p{5in}|}
\multicolumn{1}{c}{\textbf{Behavior}} &
\multicolumn{1}{c}{\textbf{Model}} &
\multicolumn{1}{c}{\textbf{Description}} \\
\hline
\multirow{3}[13]{*}{Network}
\bigstrut & \multirow{1}{*}[-0.05em]{\textbf{T}race} &
Mapping of flow end-points to wireless nodes taken directly from trace data. \\
\cline{2-3}
\bigstrut & \multirow{1}{*}[-0.05em]{\textbf{M}arginal} &
Use marginal empirical distributions from trace. \\
\cline{2-3}
\bigstrut & \multirow{1}{*}[-0.05em]{\textbf{S}ynthetic} &
Use synthetic distributions \textit{\`a la} Hern\'andez-Campos~\cite{Hernandez06:wlan-traffic}. \\
\cline{2-3}
\bigstrut & \multirow{1}{*}[-0.05em]{\textbf{U}niform} &
Both end-points are uniformly randomly chosen from all of the wireless nodes. \\
\hline
\multirow{2}[11]{*}{Flow}
\bigstrut & \multirow{1}{*}[-0.05em]{\textbf{T}race} &
Each flow has the actual start time, end time, total data sent, and number of packets from the trace. \\
\cline{2-3}
\bigstrut & \multirow{1}{*}{\textbf{P}roportional} &
Byte count taken from trace; sizes and intervals are CBR or VBR, on a per-flow basis. \\
\cline{2-3}
\bigstrut & \multirow{1}{*}{\textbf{U}niform} &
All flows have the same duration, volume, packet rate, and data rate as the trace average. \\
\hline
\multirow{2}[11]{*}{Packet}
\bigstrut & \multirow{1}{*}[-0.05em]{\textbf{T}race} &
The sequence of packet sizes and inter-transmission intervals is taken directly from the trace. \\
\cline{2-3}
\bigstrut & \multirow{1}{*}[-0.05em]{\textbf{S}ample} &
Packets sizes and intervals are randomly drawn from per-flow empirical distributions (VBR). \\
\cline{2-3}
\bigstrut & \multirow{1}{*}[-0.05em]{\textbf{U}niform} &
Packets sizes are uniform and the inter-packet interval is constant (CBR). \\
\hline
\end{tabular}

>>>>

\noindent
\textbf{Node:}
\begin{itemize}
  \item \textit{Individual}
  \begin{itemize}
    \item each node corresponds to a specific trace node with associated trace flows
    \item session start time assigned from trace
    \item overrides all distributions with per-node versions
  \end{itemize}
  \item \textit{Nonparametric}
  \begin{itemize}
    \item generic flows assigned to nodes by sampling
    \item session start time assigned from pool of start times
  \end{itemize}
  \item \textit{Parametric}
  \begin{itemize}
    \item generic flows assigned to nodes according to BiPareto model
    \item session start time randomly chosen from viable range
  \end{itemize}
  \item \textit{Uniform}
  \begin{itemize}
    \item all nodes have average number of generic flows
    \item session start times uniformly cover viable range
  \end{itemize}
\end{itemize}
\noindent
\textbf{Flow:}
\begin{itemize}
  \item \textit{Individual}
  \begin{itemize}
    \item each flow corresponds to a specific trace flow with an associated packet trace
    \item flow size \& start time taken from trace
    \item overrides distributions of size/interval packet behaviors with flow-specific versions
  \end{itemize}
  \item \textit{Nonparametric}
  \begin{itemize}
    \item flow size is sampled from inherited distribution of flow sizes
    \item start time relative to previous session flow sampled from inherited distribution
    \item inherits distributions of size/interval packet behaviors from destination node
  \end{itemize}
  \item \textit{Parametric}
  \begin{itemize}
    \item flow size is sampled from BiPareto model fitted to inherited distribution
    \item start time relative to previous session flow sampled Lognormal fitted to inherited
    \item inherits distributions of size/interval packet behaviors from destination node
  \end{itemize}
  \item \textit{Uniform}
  \begin{itemize}
    \item all flows have size equal to inherited mean
    \item average inter-flow interval used between all flows
    \item inherits distributions of size/interval packet behaviors from destination node
  \end{itemize}
\end{itemize}
\noindent
\textbf{Packet:}
\begin{itemize}
  \item \textit{Individual}
  \begin{itemize}
    \item each packet corresponds to a specific trace packet
  \end{itemize}
  \item \textit{Nonparametric}
  \begin{itemize}
    \item packet sizes and intervals are sampled from inherited distributions
  \end{itemize}
  \item \textit{Parametric}
  \begin{itemize}
    \item packet sizes and intervals are drawn from inherited parametric distributions
  \end{itemize}
  \item \textit{Uniform}
  \begin{itemize}
    \item all packet sizes and inter-packet intervals are equal to inherited mean
  \end{itemize}
\end{itemize}

### 2008-01-20 paper.tex
YAML parsing and ruby to generate properties table automatically.
Itemize-based tabels for properties & models.

@@

\begin{table*}
\begin{center}\small
\input{models.tex}
\caption{The three levels of traffic behavior and the traffic models defined for each level.}\label{tab:traffic-models}
\end{center}
\vspace{-1.75em}
\end{table*}

>>>>

\begin{table}[t]
\noindent
\begin{tabular}[t]{|l|}
\hline
\begin{minipage}[l]{3.315in}
\begin{small}
\vspace{0.8em}
\input{properties.tex}
\vspace{0.7em}
\end{small}
\end{minipage}
\\\hline
\end{tabular}
\caption{Summary of properties defined for the hierarchy of object types in the traffic object model ({\footnotesize{TOM}}).}
\end{table}

\begin{table}[t]
\noindent
\begin{tabular}[t]{|l|}
\hline
\begin{minipage}[l]{3.315in}
\begin{small}
\vspace{0.8em}
\input{models.tex}
\vspace{0.7em}
\end{small}
\end{minipage}
\\\hline
\end{tabular}
\caption{Summary of how the models at each behavioral level override or inherit properties in the traffic object model ({\footnotesize{TOM}}).}
\end{table}

@@

%\begin{table*}
%\begin{center}\small
%\input{models.tex}
%\caption{The three levels of traffic behavior and the traffic models defined for each level.}\label{tab:traffic-models}
%\end{center}
%\vspace{-1.75em}
%\end{table*}
